---
title: "Helpful insights for starting a streaming service"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Tessa Hubble
Ref1: Stellenbosch University, South Africa
Email1: 21559953\@sun.ac.za.com
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: |
  This report will offer some insight into which genres would be adavnatageous to add to a streaming service among movies and series as well as which actors signal popular films. 
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(tidyverse)
credits <- read_csv("C:\\Users\\tessa\\OneDrive\\Desktop\\Masters 2023\\Data science\\Exam\\21559953\\Question_4\\data\\credits.csv")
titles <- read_csv("C:\\Users\\tessa\\OneDrive\\Desktop\\Masters 2023\\Data science\\Exam\\21559953\\Question_4\\data\\titles.csv")

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

A streaming service has to carefully select titles that will draw users to the platform. Series and movies genres therefore present an important aspect of the service. Figure 1 and 2 show the frequency of genres among series and movies with an imdb score of above 8. For the last 10 years, drama as a genre has dominated the most popular series. The next most frequent genre among the most popular series, is comedies. Documentaries tend to come up in around 25 percent of popular series. In 2022, there appears to be a spike in the popularity of the romance genre. 


```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.ext = 'png', fig.height = 5, fig.width = 10}

source("code/plots.R")
series_genres <- transformer_df("SHOW")
series_genre_plot <- genre_plotter(series_genres, "Frequency of series genres with an imdb score of above 8")
series_genre_plot



```

Among popular movies, dramas continue to appear frequently. Documentaries and comedies also perform consistently, although at lower frequencies. Actions and animation movies tend to feature less and less among popular movies over time.

```{r Figure2, warning =  FALSE, fig.align = 'center', fig.height = 5, fig.width =10, dev = 'png'}

source("code/plots.R")
movie_genres <- transformer_df("MOVIE")
movie_genre_plot <- genre_plotter(movie_genres, "Frequency of movie genres with an imdb score of above 8")
movie_genre_plot



```

The table below shows the most popular actors, their average imdb rating and their most popular movie or series performance. It becomes clear that including series in a streaming performance is of the utmost importance. More so, including very popular series within the last two decades should bring in users to the platform. Series and movies with the following actors are likely to incentivise users to join. 

```{r Figure3, warning =  FALSE, fig.align = 'center', fig.height = 5, fig.width = 7, dev = 'png'}

source("code/plots.R")
top_actors_table <- popular_actors(popular_actors)
top_actors_table


```

From these figures it would be wise to focus on dramas and documentaries among series and movies. Series appear to have some of the highest ratings therefore a large selection of different series is important. It is also important to focus on some of the highest rated actors and their top series or movies. Regardless of how old these series may be, crowds still enjoy them.  


