---
title: "Helping You Write Academic Papers in R using Texevier"
documentclass: elsarticle
Thesis_FP: no
output:
  html_document:
    df_print: paged
  pdf_document:
    keep_tex: yes
    template: Tex/TexDefault.txt
    fig_width: 3.5
    fig_height: 3.5
Author1: Tessa Hubble
Ref1: Stellenbosch University, South Africa
Email1: 21559953\@sun.ac.za
BottomRFooter: \footnotesize Page \thepage
addtoprule: yes
addfootrule: yes
margin: 2.3
bottom: 2
top: 2.5
HardSet_layout: yes
linenumbers: no
bibliography: Tex/ref.bib
csl: "Tex/harvard-stellenbosch-university.csl"
RemovePreprintSubmittedTo: yes
Journal: Journal of Finance
toc: no
numbersections: yes
fontsize: 11pt
linestretch: 1.2
link-citations: yes
AddTitle: yes
abstract: "Some weather stats to consider before moving to the UK. \n"
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')

library(tidyverse)
weather <- read_csv("C:\\Users\\tessa\\OneDrive\\Desktop\\Masters 2023\\Data science\\Exam\\21559953\\Question_2\\data\\UKMonthly_Detailed.csv")
london <- read_csv("C:\\Users\\tessa\\OneDrive\\Desktop\\Masters 2023\\Data science\\Exam\\21559953\\Question_2\\data\\london_weather.csv")



 

```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

Figure 1 shows the number of days within each year since 1881 that fall within different temperature categories. Each year, less than 25 days have a maximum temperature of less than 0 or -17.8 degrees. However, often there are between 20 and 70 days with a maximum temperature of less than 21.1 degrees. More so, there are often years where 30 to 80 days have a minimum temperature of less than 0 degrees. 


```{r Figure1,  warning =  FALSE, fig.align = 'center', fig.cap = "Number of days a year within different temperature categories \\label{Figure1}", fig.ext = 'png', fig.height = 5, fig.width = 6}
 
source("code/plots.R")

library(lubridate)
library(zoo)

    start_date <- as.yearmon("1881-01")
    N <- 1707
    date <- data.frame(year_month = seq(start_date, length = N, by = 1/12))
    weather <- cbind(weather, date)
    
temp_df <- df_transformer(weather)
temps <- density_plotter(temp_df)
temps


```

The average extreme temperatures over the last 143 years has remained within the band of 17 and 22 degrees. The highest daily maximum per month was recorded and averaged out over a year to get the figure for each year. This graph is inidcative of the most extreme temperatures throughout a year. As you can see, these extreme warm temperatures can be considered cool days in South Africa. 

```{r Figure2, warning =  FALSE, fig.align = 'center', fig.cap = "Average extreme temperatures per year \\label{Figure2}", fig.height = 5, fig.width = 6, dev = 'png'}

source("code/plots.R")

max_temp <- df_transformer(weather)
avg_temp <- line_plotter(max_temp)
avg_temp


```

The table below shows that...

```{r Figure3, warning =  FALSE, fig.align = 'center', fig.cap = "Average weather conditions over the last three decades \\label{Figure3}", fig.height = 5, fig.width = 6, dev = 'png'}

source("code/plots.R")

weather_table <- table_formatter(london)
weather_table


```


